### 2017-02-17 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex

% ==========================
% = EXPERIMENTAL PROCEDURE =
% ==========================
\chapter{Experimental Procedure}
\label{chap:Experimental_Procedure}
A similar procedure was followed for all experiments described in this report. First, three propane burners were ignited in sequential order. Next, various actions, such as opening and closing doors and roof vents or turning on a fan, were performed to change the ventilation pattern within the structure. Finally, the burners were turned off and the fire was extinguished. The nine tests were conducted in series with a variety of other experiments. In order to be consistent with the original test numbering, the experiments are referred to as Tests~2--6 and Tests~22--25 throughout this report.

>>>>

% ==========================
% = EXPERIMENTAL PROCEDURE =
% ==========================
\chapter{Experimental Procedure}
\label{chap:Experimental_Procedure}
A similar procedure was followed for all experiments described in this report. First, three propane burners were ignited in sequential order. Next, various actions, such as opening and closing doors and roof vents or turning on a fan, were performed to change the ventilation pattern within the structure. Finally, the burners were turned off and the fire was extinguished. The nine tests were conducted in series with a variety of other experiments. In order to be consistent with the original test numbering, the gas burner experiments presented in this report are referred to as Tests~2--6 and Tests~22--25.
